Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and correlation with baryon disk properties

### 2019-07-17 Document/paper.tex
caption figure 3

\begin{figure*}
\subfloat[DMO simulations.]{\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_DM.pdf}}
\subfloat[MHD simulations.]{\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_MHD.pdf}}
\caption{Cumulative fraction for the triaxiality at five different radii.
  Right/left panel correspond to DM/MHD
  simulations respectively. 
  This quantifies the main trends we find: in DM only simulations
  rounder in the outskirts, halos in MHD are rounder than DM only, and
  in MHD simulations halos tend to be rounder at the inner regions
  than its outskirts.}
\label{fig:triaxial_cumulative}
\end{figure*}

>>>>

\begin{figure*}
\subfloat[DMO simulations.]{\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_DM.pdf}}
\subfloat[MHD simulations.]{\includegraphics[width=0.9\columnwidth]{triaxialiy_distro_MHD.pdf}}
\caption{Cumulative distribution for the triaxiality at five different radii.
  Right/left panel correspond to DMO/MHD simulations, respectively. 
  In DMO simulations the median triaxiality at all radii is larger
  than $0.5$; only for $20\%$ the triaxility is smaller than $0.5$.
  Furthermore, the triaxility increases as one moves towards the inner
  part of the halo.
  In MHD simulations the situation is reversed.
  The median triaxility at all radii is smaller than $0.5$.
  Moving towards the stellar disk the triaxility decreases towards a median
  value of $T=0.15$.}
\label{fig:triaxial_cumulative}
\end{figure*}
